\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix2019_v3}

\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{enumitem}

%-------------------------------------------------------------------------------
\begin{document}
%-------------------------------------------------------------------------------

\date{}

\title{\Large \bf From Attack Surface to Psychiatric Diagnosis:\\
  A Security Framework for Brain-Computer Interfaces}

% DOUBLE-BLIND: Authors removed for review
\author{
{\rm Anonymous}
}

\maketitle

%-------------------------------------------------------------------------------
\begin{abstract}
%-------------------------------------------------------------------------------
Brain-computer interfaces (BCIs) are transitioning from experimental tools to
commercially deployed medical devices. Yet no security framework accounts for
the unique risks of devices that read and write neural signals. The Common
Vulnerability Scoring System (CVSS v4.0) cannot express biological tissue
damage, cognitive integrity violations, or consent boundaries---dimensions
critical to neural device security.

We present an integrated framework with four contributions:
(1)~an 11-band hourglass architecture mapping attack surfaces from neocortex
to wireless radio;
(2)~a threat taxonomy of 102 techniques across 15 tactics and 8 domains;
(3)~a CVSS v4.0 extension adding five neural-specific metrics; and
(4)~a methodology mapping security vulnerabilities to DSM-5-TR psychiatric
diagnoses.

Analysis reveals that 94.4\% of catalogued techniques require neural-specific
metrics that CVSS cannot express, and 51 techniques pose direct psychiatric
diagnostic risk. We validate the framework through two vulnerability
disclosures against real BCI-adjacent systems. The complete framework is
released as open source.
\end{abstract}

\input{sections/01-introduction}
\input{sections/02-related-work}
\input{sections/03-architecture}
\input{sections/04-taxonomy}
\input{sections/05-scoring}
\input{sections/06-impact-chain}
\input{sections/07-case-studies}
\input{sections/08-ethics}
\input{sections/09-limitations}
\input{sections/10-conclusion}

%-------------------------------------------------------------------------------
\section*{Availability}
%-------------------------------------------------------------------------------

The complete framework, threat registry, and scoring system are released
as open source under the Apache 2.0 license.%
\footnote{Repository URL withheld for double-blind review.}
An interactive threat registry browser and scoring calculator are available
at the project website.

%-------------------------------------------------------------------------------
\bibliographystyle{plain}
\bibliography{references}

\end{document}
